### 2019-09-25 reports/thesis/chapters/5_inference.tex
Revise and used proofreader

\begin{figure}
  \centering
  \includegraphics[width=\subSize]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
  \caption{The density of the test statistics, from Figure \ref{fig:inference_inferenceSubsample1_histogram}, was estimated using a kernel density estimate. The dot dashed line shows the empirical null distribution multiplied by some constant, this is to illustrate that the two densities have the same curvature at the mode.}
  \label{fig:inference_inferenceSubsample1_densityEstimate}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error1.eps}
      \caption{$\mu_0$}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error2.eps}
      \caption{$\sigma_0$}
  \end{subfigure}
  \caption{Median squared error of the estimates of the empirical null parameters over 100 repeats of $n$ simulated standard Normal data. Lines represent the rule of thumb for various values of $b$.}
  \label{fig:inference_BandwidthSelection_error}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\mainSize]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experiment. The dashed lines shows the 68\% prediction interval.}
  \label{fig:inference_BandwidthSelection2_ruleOfThumb}
\end{figure}

\begin{table}
  \centering
  \begin{tabular}{l|c}
           &Estimate \\ \hline
  Intercept&\input{../figures/inference/BandwidthSelection2_coeff1.txt}\\
  Gradient &\input{../figures/inference/BandwidthSelection2_coeff2.txt}
  \end{tabular}
  \caption{Estimated and standard error of the gradient and intercept from the linear relationship in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb}.}
  \label{table:inference_BandwidthSelection2_ruleOfThumb}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/inference/fiji/gui.png}
    \caption{Graphical user interface of the empirical null filter in \emph{Fiji}. The user can adjust the kernel radius as well as other advanced options relating to the Newton-Raphson method and the kernel density estimate. By-products such as the empirical null parameters can be shown after the filtering as well.}
    \label{fig:inference_fijiGui}
\end{figure}

@@

The empirical null filter was tested to see if it can assist in detecting simulated defects from an image with/without contamination. A defect assign pixels to have a value not distributed under the null distribution, but instead, under an alternative, or non-null, distribution. For example, suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect assign certain pixels to have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_roc.eps}
        \caption{Dust defect, $r=\SI{20}{\pixel}$}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_roc.eps}
        \caption{Line defect, $r=\SI{20}{\pixel}$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_roc.eps}
        \caption{Square defect, $r=\SI{20}{\pixel}$}
        \label{fig:inference_defectSimulationRoc_square20}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_roc.eps}
        \caption{Square defect, $r=\SI{40}{\pixel}$}
      \end{subfigure}
    }
  \caption{ROC curves for various defected $\SI{256}{\pixel}\times \SI{256}{\pixel}$ Gaussian images. The upper/lower dot dashed lines show the resulting ROC curve when testing on an image without/with contamination respectively. The different curves are the resulting ROC curves after filtering a contaminated image. The speckle defect has density $\pi_1=0.1$. The line defect is \SI{5}{\pixel} thick. The square defect is $\SI{30}{\pixel}\times \SI{30}{\pixel}$ in size. Defected pixels have the distribution $\normal(3,1)$. The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
  \label{fig:inference_defectSimulationRoc}
\end{figure}

@@

The ROC curves consider all thresholds or specificities used in the hypotheses testing. In the previous experiment, it was found that the variance of the test statistics were different before and after filtering. As a result, for a given threshold, such as the 5\% FDR level, the specificity may change ever so slightly after filtering.

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
        \caption{Type 1 error}
        \label{fig:inference_DefectSimulationDust_type1}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
        \caption{FDR}
        \label{fig:inference_DefectSimulationDust_fdr}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypotheses testing on an empirical null filtered contaminated salt defected Gaussian image of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$. In a), the upper/lower dot dashed lines shows the resulting mean AUC when testing on a defected image before/after contamination respectively. In b), c) and d), the dashed lines show the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination. The filter used a kernel radius of \SI{20}{\pixel}. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The boxplots summarise the 100 repeated simulations of the image.}
  \label{fig:inference_DefectSimulationDust}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.eps}
      \caption{$z$ image with section highlighted}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHist.eps}
      \caption{Histogram of $z$ in the kernel}
    \end{subfigure}
  }
  \caption{A section of the bottom right of a unfiltered $z$ image is shown in a). The $z$ statistics in it are shown as a histogram in b) and indicates a bimodal distribution.}
  \label{fig:inference_cornerSelect}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\subSize]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
  \caption{The density of the test statistics, from Figure \ref{fig:inference_inferenceSubsample1_histogram}, was estimated using a kernel density estimate. The dot-dashed line shows the empirical null distribution multiplied by some constant, this is to illustrate that the two densities have the same curvature at the mode.}
  \label{fig:inference_inferenceSubsample1_densityEstimate}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error1.eps}
      \caption{$\mu_0$}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error2.eps}
      \caption{$\sigma_0$}
  \end{subfigure}
  \caption{The median squared error of the estimates of the empirical null parameters over 100 repeats of $n$ simulated standard Normal data. Lines represent the rule of thumb for various values of $b$.}
  \label{fig:inference_BandwidthSelection_error}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\mainSize]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experiment. The dashed lines show the 68\% prediction interval.}
  \label{fig:inference_BandwidthSelection2_ruleOfThumb}
\end{figure}

\begin{table}
  \centering
  \begin{tabular}{l|c}
           &Estimate \\ \hline
  Intercept&\input{../figures/inference/BandwidthSelection2_coeff1.txt}\\
  Gradient &\input{../figures/inference/BandwidthSelection2_coeff2.txt}
  \end{tabular}
  \caption{The estimated and standard error of the gradient and intercept from the linear relationship in Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb}.}
  \label{table:inference_BandwidthSelection2_ruleOfThumb}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/inference/fiji/gui.png}
    \caption{The graphical user interface of the empirical null filter in \emph{Fiji}. The user can adjust the kernel radius as well as other advanced options relating to the Newton-Raphson method and the kernel density estimate. By-products such as the empirical null parameters can be shown after the filtering as well.}
    \label{fig:inference_fijiGui}
\end{figure}

@@

The empirical null filter was tested to see if it can assist in detecting simulated defects from an image with/without contamination. A defect assigns pixels to have a value not distributed under the null distribution, but instead, under an alternative, or non-null, distribution. For example, suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect assign certain pixels to have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_roc.eps}
        \caption{Dust defect, $r=\SI{20}{\pixel}$}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_roc.eps}
        \caption{Line defect, $r=\SI{20}{\pixel}$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_roc.eps}
        \caption{Square defect, $r=\SI{20}{\pixel}$}
        \label{fig:inference_defectSimulationRoc_square20}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_roc.eps}
        \caption{Square defect, $r=\SI{40}{\pixel}$}
      \end{subfigure}
    }
  \caption{ROC curves for various defected $\SI{256}{\pixel}\times \SI{256}{\pixel}$ Gaussian images. The upper/lower dot-dashed lines show the resulting ROC curve when testing on an image without/with contamination respectively. The different curves are the resulting ROC curves after filtering a contaminated image. The speckle defect has density $\pi_1=0.1$. The line defect is \SI{5}{\pixel} thick. The square defect is $\SI{30}{\pixel}\times \SI{30}{\pixel}$ in size. Defected pixels have the distribution $\normal(3,1)$. The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
  \label{fig:inference_defectSimulationRoc}
\end{figure}

@@

The ROC curves consider all thresholds or specificities used in the hypotheses testing. In the previous experiment, it was found that the variance of the test statistics was different before and after filtering. As a result, for a given threshold, such as the 5\% FDR level, the specificity may change ever so slightly after filtering.

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
        \caption{Type 1 error}
        \label{fig:inference_DefectSimulationDust_type1}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
        \caption{FDR}
        \label{fig:inference_DefectSimulationDust_fdr}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypotheses testing on an empirical null filtered contaminated salt defected Gaussian image of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$. In a), the upper/lower dot-dashed lines shows the resulting mean AUC when testing on a defected image before/after contamination respectively. In b), c) and d), the dashed lines show the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination. The filter used a kernel radius of \SI{20}{\pixel}. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination was such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The boxplots summarise the 100 repeated simulations of the image.}
  \label{fig:inference_DefectSimulationDust}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/cornerSelect.eps}
      \caption{$z$ image with section highlighted}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/cornerSelectHist.eps}
      \caption{Histogram of $z$ in the kernel}
    \end{subfigure}
  }
  \caption{A section of the bottom right of an unfiltered $z$ image is shown in a). The $z$ statistics in it are shown as a histogram in b) and indicates a bimodal distribution.}
  \label{fig:inference_cornerSelect}
\end{figure}
